LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-07 main.tex
Use hyperref package

\usepackage{amsmath}
\usepackage{commath}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{cleveref}

@@

@@

The altimeter products used in this work are produced by SSALTO/DUACS and distributed by AVISO, with support from CNES, http://www.aviso.oceanobs.com/duacs.

>>>>

\usepackage{amsmath}
\usepackage{commath}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

% Workaround for bug in elsarticle-num-names.bst
% Reference: http://www.tug.org/pipermail/tex-live/2012-August/032152.html
\makeatletter
\providecommand{\doi}[1]{%
  \begingroup
    \let\bibinfo\@secondoftwo
    \urlstyle{rm}%
    \href{http://dx.doi.org/#1}{%
      doi:\discretionary{}{}{}%
      \nolinkurl{#1}%
    }%
  \endgroup
}
\makeatother

@@

\begin{sloppypar}
The altimeter products used in this work are produced by SSALTO/DUACS and distributed by AVISO, with support from CNES, \url{http://www.aviso.oceanobs.com/duacs}.
\end{sloppypar}
